---
title: "haigh"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(haven)
library(psych)
library(ggpubr)
library(PupillometryR)
library(ggeasy)
library(yarrr)
```

- I ran the first part of Study 8 Script.R to get the tidied data 
- used the tidied data set for experiment 2
```{r}
exp1_tidy <- read_csv(here("haigh", "exp 1", "MyDataTidied.csv"))

n_exp1 <- length(unique(exp1_tidy$X1)) # 294 participants

exp1 <- exp1_tidy %>%
  clean_names() 


exp2_tidy <- read_csv(here("haigh", "exp 2", "study7_tidy.csv"))

n_exp2 <- length(unique(exp2_tidy$X1))

exp2 <- exp2_tidy %>%
  clean_names() 
  
```

# Demographics Study 1
- 1 = males
- 2 = females
```{r}
demo <- exp1 %>%
  select(gender, age)

describe(demo$age)

demo %>% 
  group_by(gender) %>%
  count()

```

# Demographics Study 2
- 1 = male
- 2 = female 
- 3 = other
```{r}
demo2 <- exp2 %>%
  select(gender, age)

describe(demo2$age)

demo2 %>% 
  group_by(gender) %>%
  count()
```

# Figure 1 - violin plot
- experiment 1
- perceived contracdiction appears to be sum of all 6 contradiction responses not mean
- violin plot is right
- boxplot is not right
```{r}
glimpse(exp1_tidy)

exp1_tidy$condition <- factor(exp1_tidy$condition, labels = c("Generic Conflict", "Generic Non-Conflict", "Qualified Conflict", "Qualified Non-Conflict"))
levels(exp1_tidy$condition)

fig1 <- exp1_tidy %>%
  select(condition, contradiction_1:contradiction_6, confusion, advancement) %>%
  mutate(sum_contra = contradiction_1+contradiction_2+contradiction_3+contradiction_4+contradiction_5+contradiction_6,
         format = ifelse((condition == "Generic Conflict" | condition == "Generic Non-Conflict"), "Generic", "Qualified"), 
         conflict = ifelse((condition == "Generic Conflict" | condition == "Qualified Conflict"), "Conflict", "Non-Conflict")) 

fig1 %>%
  group_by(conflict) %>%
  summarise(mean_contradict = mean(sum_contra), 
            mean_confusion = mean(confusion), 
            mean_advancement = mean(advancement))

ggplot(fig1, aes(condition, sum_contra, fill = conflict)) +
  geom_violin(alpha = .5) +
  geom_point() +
  labs(x = "", y = "Perceived Contradiction") +
  theme_classic() +
  easy_text_size(15) +
  easy_remove_legend()

ggplot(fig1, aes(condition, advancement, fill = conflict)) +
  geom_violin(alpha = .5) +
  geom_point() +
  labs(x = "", y = "Perceived Scientific Advancement") +
  theme_classic() +
  easy_text_size(15) +
  easy_remove_legend()

ggplot(fig1, aes(condition, confusion, fill = conflict)) +
  geom_violin(alpha = .5) +
  geom_point() +
  labs(x = "", y = "Perceived Confusion") +
  theme_classic() +
  easy_text_size(15) +
  easy_remove_legend()

```

# Figure 1 - Pirate plots
- took this code from the authors script but adjusted for my dataset 
```{r}
pirateplot(formula = sum_contra ~ conflict*format, data = fig1,inf.method = 'ci', yaxt = "n", ylim =c(0,30), theme=1,main = "Contradiction", ylab = "Percieved Contradiction",cex.names = 0.75, cex.lab = 0.9)
axis(2, at = seq(from = 0, to = 30, by = 5)) 

plot.new()

pirateplot(formula = advancement ~ conflict*format, data = fig1,inf.method = 'ci', yaxt = "n", theme=1,main = "Advancement", ylab = "Percieved Scientific Advancement",cex.names = 0.75, cex.lab = 0.9)
axis(2, at = seq(from = -1, to = 1, by = 1))

plot.new()

pirateplot(formula = confusion ~ conflict*format, data = fig1,inf.method = 'ci', yaxt = "n", theme=1,main = "Confusion", ylab = "Percieved Confusion",cex.names = 0.75, cex.lab = 0.9)
axis(2, at = seq(from = 1, to = 5, by = 1)) 
```

# Figure 2
- still exp1
- from author's script I found labels for advancement -1=less, 0=same, 1=more
```{r}
glimpse(exp1)
fig1$advancement <- factor(fig1$advancement, 
                           labels = c("Less", "Same", "More"))
fig1$condition <- factor(fig1$condition, 
                           levels = c("Generic Conflict", "Qualified Conflict", "Generic Non-Conflict", "Qualified Non-Conflict"))


ggplot(fig1,aes(x=advancement, group=condition,fill=condition)) + #set to group by 4 conditions
  geom_bar(position="dodge") + 
  labs(x="Advancemnt", y="Number of Participants") +
  scale_fill_grey(start = 0, end = .8) +
  theme_classic()
    
```

# Figure 3 
- haven't tried yet but looks the same as Fig 1