---
title: "QnA Session Week 6"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# load libraries
```{r}
library(tidyverse)
library(here)
library(janitor)
library(gt)
library(haven)
require(gridExtra)
library(ggeasy)
library(gtsummary)
library(cowplot) # for ggdraw()
library(extrafont)
loadfonts(device="win") 
```

# eval = FALSE

- here's an example where the code will produce an error
- but we can still knit the document because eval is set to FALSE
```{r eval = FALSE}
# I made a typo here (should be read_csv!)
group1 <- read_cvs(here("data", "1_carstensen", "AgeAdvantagesEmotionCovid_Data.csv")) 
```

# Formatting Tables!

- gt package
- I found this website helpful: [http://www.danieldsjoberg.com/gt-and-gtsummary-presentation/#12](http://www.danieldsjoberg.com/gt-and-gtsummary-presentation/#12)

[https://gt.rstudio.com/articles/intro-creating-gt-tables.html](https://gt.rstudio.com/articles/intro-creating-gt-tables.html)

- hide columns
- format numbers
- format %
- merge 2 columns together
- format currency
- add footnote
```{r eval=TRUE}
# exibble (example tibble) is part of the gt package

# I'm adding a couple of extra columns to demonstrate what we can do with gt
my_table <- exibble %>%
  mutate(perc = c(10, 20, 30, 40, 50, 60, 70, 80), 
         sd = c(.1, .1, .25, .2, .1, .1, .3, .25))


my_table %>%
  gt(
    rowname_col = "row",
    groupname_col = "group"
  ) %>%
  cols_hide( # hide columns
    columns = vars(date, time, fctr, char, datetime) # make sure to use vars()
  ) %>%
  fmt_number( # format numbers to 2 decimal places
    columns = vars(num), 
    decimals = 2
  ) %>%
  fmt_number( ### get parentheses!
    columns = vars(sd),
    pattern = "({x})"
  )  %>%
  fmt_percent( # format percent
    columns = vars(perc), 
    scale_values = FALSE, # by default this is set to try which multiplies the variable by 100
    decimals = 0
  ) %>%
  cols_merge( # merge columns into 1
     columns = vars(perc, sd) #,
    # pattern = "{1} ({2})" # or this also works to add parentheses in columns you are merging
  ) %>%
  cols_label( # added this
    perc = "% (sd)",
  ) %>%
  fmt_currency( # add currency 
    columns = vars(currency),
    currency = "AUD"
  ) %>%
  tab_header( # title and subtitle
    title = md("Example Table from **exibble**"), # md is to allow markdown formatting
    subtitle = md("`exibble` is an gt dataset")
  ) %>%
  tab_footnote( # you can add 1 or more footnotes
    footnote = "These are lower prices", 
    locations = cells_body(
      columns = vars(currency), 
      rows = currency < 15
    )
  ) %>%
  tab_footnote(
    footnote = "These big numbers", 
    locations = cells_body(
      columns = vars(num), 
      rows = num > 500
    )
  )

```

# example covid table

- note: I'm not including the code here in case group 4 wants to try to reproduce a similar table themselves!
```{r echo=FALSE}
library(haven)

group4 <- read_sav(here("data","8_smith",  "believing.sav")) %>%
  clean_names() %>%
  rowid_to_column("ID")

# example from group 4 
# if you're not in group 4, don't worry too much about this first bit of code, it's just to create a dataset for us to explore gt and creating pretty tables!
group4_dems_labs <- group4 %>% 
  select(ever_covid, gender:region, -has_child) 

group4_dems <- zap_labels(group4_dems_labs) %>% # removed labels 
    mutate_if(is.numeric, as.factor) # turn numeric variables into factors

# changing lables 
group4_dems$ever_covid <- factor(group4_dems$ever_covid, labels = c("no_covid", "yes_covid"))

group4_dems$gender <- factor(group4_dems$gender, labels = c("Male", "Female"))

group4_dems$degree <- factor(group4_dems$degree, labels = c("No formal qualifications", "Degree or higher"))

group4_dems$age_categories <- factor(group4_dems$age_categories, labels = c("18 to 24 years", "25 to 34 years", "35 to 44 years", "45 to 54 years", "55 years and over"))

group4_dems$region <- factor(group4_dems$region, labels = c("Midlands", "South & East", "North", "London", "Wales, Scotland, N. Ireland"))

group4_table <- group4_dems %>%
  pivot_longer(!ever_covid, names_to = "vars", values_to = "values") %>%
  group_by(ever_covid, vars, values) %>%
  count(name = "number") %>%
  filter(vars %in% c("age_categories", "gender", "degree", "region" )) %>%
  na.omit() %>%
  group_by(vars,values) %>%
  mutate(percentage = round(number/sum(number) * 100, 1))

# let's turn our dataset into a table with the gt() function! 
tab1 <- group4_table %>%
  gt() 

# here's an example of where pivot_wider can come in handy, we want one column for "no covid" and one column for "yes column"
table_new <- group4_table %>%
  pivot_wider(names_from = ever_covid, values_from = c(number, percentage)) %>%
  clean_names()  %>%
  ungroup() %>%
  relocate(vars, values, number_no_covid, percentage_no_covid, number_yes_covid, percentage_yes_covid) %>% # reorders columns
  mutate(percentage_no_covid = paste0("(",percentage_no_covid, "%)"), # add ( %)
         percentage_yes_covid = paste0("(",percentage_yes_covid, "%)"))

table_new$vars <- as.factor(table_new$vars)
table_new$vars <- factor(table_new$vars, levels = c("gender", "age_categories", "degree", "region"), labels = c("Gender", "Age", "Highest Educational Qualification", "Region"))

table_new %>%
  gt(
    groupname_col = "vars",
    rowname_col = "values"
  )  %>%
    row_group_order( # can reorder the variables in the table
      groups = c("Gender", "Age", "Highest Educational Qualification", "Region")
    ) %>%
  cols_merge( # merge columns with the number and percentage
    columns = vars(number_no_covid, percentage_no_covid)
  ) %>%
  cols_merge(
    columns = vars(number_yes_covid, percentage_yes_covid)
  )  %>%
  tab_spanner( # can add a section header that spans across multiple columns
    label = "Had COVID-19",
    columns = vars(number_no_covid, number_yes_covid) # specify which columns it spans across
  ) %>%
  tab_style( # add styling, here I want the group names to be bold
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  )  %>%
  tab_style( # add styling, here I want the group names to be bold
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(columns = everything()) # everything() or vars(number_no_covid, number_yes_covid)
  )  %>%
  tab_style( # add styling, here I want the group names to be bold
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners(spanners = everything())
  )  %>%
  cols_label( # can easily rename your variables within gt
    number_no_covid = "Think have not had
COVID-19",
    number_yes_covid = "Think have had
COVID-19"
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "#D7D7D7")
    ),
    locations = cells_body(
      rows = c(1,3,5,7,9,11,13))
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "#D7D7D7")
    ),
    locations = cells_stub(
      rows = c(1,3,5,7,9,11,13))
  )
```

# correlation example
```{r eval = FALSE}
corr_ex <- iris %>%
  as_tibble() %>%
  clean_names()

# get correlation coefficient
cor(corr_ex$sepal_length, corr_ex$petal_width)

# get correlation coefficient + p value
cor.test(corr_ex$sepal_length, corr_ex$petal_width)
```

# Group 5 

- how to know if someone is single or married?... doesn't look like you can
- sort in descending order by country by sample size
- exclude countries sample size less than 15
```{r eval=FALSE}
group5 <- read_csv("data/9_folk/Study2.csv") %>%
  clean_names()

group5 %>%
  select(country, participant_id) %>%
  group_by(country) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(n > 14)

group5 %>%
  group_by(country) %>%
  summarise(sample_size = size_sum(country))

group5 %>%
  group_by(country) %>%
  summarise(sample_size = n(), # I like this function better but does the same thing that you have
            mean_social_distance = mean(social_distancing)*100, 
            mean_six_feet = mean(six_feet),
            sd_six_feet = sd(six_feet)) %>% # you need a separate line for this
  ungroup()
```

- issues with sd values for age variable being NA (example with social distance variable)
- mean and sd show up in the same column 
- example of merging columns
```{r eval=FALSE}
group5 %>%
  select(country, participant_id) %>%
  group_by(country) %>%
  count() %>%
  arrange(n)

# even if you include na.rm = TRUE, you'll still see NAs
# the problem is some countries only have 1 observation, so if that 1 value is NA it will be NA even with na.rm
group5 %>%
  select(country, social_distancing) %>%
  group_by(country) %>%
  summarise(mean_soc_dist = mean(social_distancing, na.rm = TRUE),
            sd_soc_dist = sd(social_distancing, na.rm = TRUE))

# we can exclude countries/observation with NAs 
merg_col <- group5 %>%
  select(country, social_distancing) %>%
  group_by(country) %>%
  summarise(mean_soc_dist = mean(social_distancing, na.rm = TRUE),
            sd_soc_dist = sd(social_distancing, na.rm = TRUE)) %>%
  na.omit()

merg_col %>%
  gt() %>%
  fmt_number(
    columns = vars(mean_soc_dist, sd_soc_dist),
    decimals = 2
  ) %>%
  cols_merge(
    columns = vars(mean_soc_dist, sd_soc_dist)
  ) %>%
  cols_label(
    mean_soc_dist = "Mean & SD"
  )

```

# Group 2

- grid.arrange 3 plots together: common x and y axis labels 
- reorder/relevel factors *fct_relevel*
```{r eval=FALSE}
group2 <- iris %>%
  as_tibble() %>%
  clean_names()

setosa <- group2 %>%
  filter(species == "setosa")
versicolor <- group2 %>%
  filter(species == "versicolor")
virginica <- group2 %>%
  filter(species == "virginica")

plot1 <- ggplot(setosa, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw()

plot2 <- ggplot(versicolor, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw()

plot3 <- ggplot(virginica, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw()

grid.arrange(plot1, plot2, plot3, ncol=3)

plot1 <- ggplot(setosa, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(x = "", y = "")

plot2 <- ggplot(versicolor, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(x = "", y = "")

plot3 <- ggplot(virginica, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(x = "", y = "")

grid.arrange(plot1, plot2, plot3, ncol=3, left = "Sepal Width", bottom = "Sepal Length")

# OR combine all data into one dataset and plot it all together
# only 5 lines of code this way!

ggplot(group2, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  facet_wrap(~species) +
  theme_bw() +
  labs(x = "Sepal Length", y = "Sepal Width")

## reorder factors 
# right now it's in alphabetical order
# I want versicolor, setosa, virginica 
levels(group2_ex$species)

group2_ex$species <- fct_relevel(group2_ex$species, c("versicolor", "setosa", "virginica"))

ggplot(group2_ex, aes(x=sepal_length, y=sepal_width)) +
  geom_smooth(method = "lm") + 
  facet_wrap(~species) +
  theme_bw() 
``` 

# Group 3 

- change font: Thomas's Learning Log 
- add x and y axis lines 
- add dotted lines between studies
- adjust width of individual plots when combining plots together
```{r eval=FALSE}
group3 <- iris %>%
  as_tibble() %>%
  clean_names()

p <- ggplot(group3, aes(sepal_length, sepal_width)) +
  geom_smooth(method = "lm") +
  facet_grid(~species) +
  theme_minimal() +
  theme(
    axis.line = element_line(colour= "black"),
    panel.spacing = unit(2, "lines")
  )

ggdraw() +
  draw_plot(p) +
  draw_line(
    x = c(0.7, 0.7),
    y = c(0.1, 0.9),
    color = "lightgrey", size = 2, linetype = 2
  ) +
  draw_line(
    x = c(0.35, 0.35),
    y = c(0.1, 0.9),
    color = "lightgrey", size = 2, linetype = 2
  )

```

# Group 4 

- this is the same code I posted last week
- unfortunately, for your question I needed to see your code but no one from group 4 was at Thursday's session 
- try going through this code again and let me know if you still have issues
```{r eval=FALSE}
group4 <- read_sav(here("data","8_smith",  "believing.sav")) %>%
  clean_names() %>%
  rowid_to_column("ID")

# example from group 4 
# if you're not in group 4, don't worry too much about this first bit of code, it's just to create a dataset for us to explore gt and creating pretty tables!
group4_dems_labs <- group4 %>% 
  select(ever_covid, gender:region, -has_child) 

group4_dems <- zap_labels(group4_dems_labs) %>% # removed labels 
    mutate_if(is.numeric, as.factor)

group4_dems$ever_covid <- factor(group4_dems$ever_covid, labels = c("no_covid", "yes_covid"))

group4_dems$gender <- factor(group4_dems$gender, labels = c("Male", "Female"))

group4_dems$degree <- factor(group4_dems$degree, labels = c("No
formal qualifications", "Degree or higher"))

group4_dems$age_categories <- factor(group4_dems$age_categories, labels = c("18 to 24 years", "25 to 34 years", "35 to 44 years", "45 to 54 years", "55 years and over"))

group4_dems$region <- factor(group4_dems$region, labels = c("Midlands", "South & East", "North", "London", "Wales, Scotland, N. Ireland"))

group4_table <- group4_dems %>%
  pivot_longer(!ever_covid, names_to = "vars", values_to = "values") %>%
  group_by(ever_covid, vars, values) %>%
  count(name = "number") %>%
  filter(vars %in% c("age_categories", "gender", "Has_child", "Working", "Key_worker", "degree", "region" )) %>%
  na.omit %>%
  group_by(vars,values) %>%
  mutate(percentage = round(number/sum(number) * 100, 1))

# let's turn our dataset into a table with the gt() function! 
group4_table %>%
  gt() 

# here's an example of where pivot_wider can come in handy, we want one column for "no covid" and one column for "yes column"
table_new <- group4_table %>%
  pivot_wider(names_from = ever_covid, values_from = c(number, percentage)) %>%
  clean_names()  %>%
  ungroup() %>%
  relocate(vars, values, number_no_covid, percentage_no_covid, number_yes_covid, percentage_yes_covid) # reorders columns

table_new %>%
  gt()
```

