---
title: "References"
output: 
   prettydoc::html_pretty:
     theme: cayman
bibliography: all_references.bib  
---

# install [citr](https://github.com/crsh/citr)
```{r eval = FALSE}
devtools::install_github("crsh/citr")
```

- close and reopen Rstudio
- check to see if "insert citations" is now in your addins 
- click on it and it should run the following code:

```{r eval = FALSE}
citr:::insert_citation()
```

# create a .bib file with your references stored 

- I do this by going to google scholar, searching for the article I want to cite, clicking on the quotation symbol, and selecting BibTex
- copy the bibtex file
- open up a new R script and paste the bibtex file
- make sure to save this as a .bib file (e.g. myrefs.bib)
- add all the references you want to this file 
- you may have to close and reopen Rstudio once more

# include bibliography: xxxx.bib in your heading (e.g. bibliography: myrefs.bib)

- test it out! 
- for parenthetical citations, check include parentheses 
- for in text citations, uncheck that option

[@Tybur2020] - "in parentheses" is checked <br>
@Tybur2020 - "in parentheses" is not checked




