---
title: "QnA Week 10"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(ggeasy)
library(janitor)
library(here)
library(haven)

# tinytex::install_tinytex()
#tinytex::tlmgr_install("pdfcrop") # to knit to pdf
# https://bookdown.org/yihui/rmarkdown/pdf-document.html
```

# knitting to PDF
- See notes [here](https://rpubs.com/jsloane/knit_pdf_word)

# Trouble shooting tips
- go through code line by line to try to find exactly where you're problem is
- look at your dataset before you begin adding pipes to it to make sure you have all the variables you need 

# Should graphs use summarised data?

- while you certainly can create graphs using summarised data, I think it's often better to create graphs with the full dataset 
- example to show you why 

## create graph using summarise function 

```{r}
library(readxl)
study4 <- read_excel("data/3_pfattheicher/Study4.xlsx") %>%
  rowid_to_column("ID") %>%
  zap_labels()

stats_ex <- study4 %>%
  filter(bed == 2) %>%
  select(ID, Age, empa) %>%
  mutate(age_group = case_when(
    Age < 20 ~ "Teens",
    Age > 19 & Age < 30 ~ "Twenties",
    Age > 29 & Age < 40 ~ "Thirties",
    Age > 39 & Age < 50 ~ "Fourties",
    Age > 49 & Age < 60 ~ "Fifties",
    Age > 59 ~ "Elderly")
  ) %>%
  group_by(age_group) %>%
  summarise(mean_emp = mean(empa))

stats_ex$age_group <- fct_relevel(stats_ex$age_group,
  c("Teens", "Twenties", "Thirties", "Fourties", "Fifties", "Elderly"))
levels(stats_ex$age_group)

ggplot(stats_ex, aes(age_group, mean_emp, fill=age_group)) +
  geom_col() # this graph is okay, but it's missing some useful information such as error bars 
```

## create graph WITHOUT summarise function 
```{r}
# create graph using all of the data (no summarising), same code just withouth group_by and summarise()
stats_ex2 <- study4 %>%
  filter(bed == 2) %>%
  select(ID, Age, empa) %>%
  mutate(age_group = case_when(
    Age < 20 ~ "Teens",
    Age > 19 & Age < 30 ~ "Twenties",
    Age > 29 & Age < 40 ~ "Thirties",
    Age > 39 & Age < 50 ~ "Fourties",
    Age > 49 & Age < 60 ~ "Fifties",
    Age > 59 ~ "Elderly")
  ) 

stats_ex2$age_group <- fct_relevel(stats_ex2$age_group,
  c("Teens", "Twenties", "Thirties", "Fourties", "Fifties", "Elderly"))
levels(stats_ex2$age_group)

ggplot(stats_ex2, aes(age_group, empa, fill=age_group)) +
  geom_boxplot() + # now we can use boxplot! much more informative 
  stat_summary(fun="mean")
```


# Anova question

- stats - compare means of multiple groups... ANOVA 
- always use the full dataset when running a model/analysis
```{r}
# what happens if we try to run an anova on this summarised data
aov_test <- aov(mean_emp~age_group, stats_ex)
summary(aov_test) # something is not right here...


aov_test2 <- aov(empa~age_group, stats_ex2) # now our model has all of the data points so this will work
summary(aov_test2)
```


## Error message 

- tip if you get an error message: run your code line by line to find exactly where the problem is 
- if you find your problem is within a long string of pipes, go through your pipe piece by piece

# Combining multiple datasets
```{r}
data_1_raw = read_csv('data/4_tybur/WTR_Comfort_S1.csv')
data_2 = read_csv('data/4_tybur/WTR_Comfort_S2.csv')
data_3 = read_csv('data/4_tybur/WTR_Comfort_S3.csv')

# select which columns we want 
data1 <- data_1_raw %>%
  select(participant, sex, age, income, DS1)

data2 <- data_2 %>%
  select(participant, sex, age, income, DS1)

data3 <- data_3 %>%
  select(participant, sex, age, income, DS1)

# combine data together (this is assuming participants are different in each study)
data_all <- rbind(data1, data2, data3)
```

# stacked bar plot and how to round 
```{r}
# how to round
COVID <- read_sav(here("data","8_smith",  "believing.sav")) %>%
  rowid_to_column("ID")

COVIDexplore1 <- COVID %>%
  mutate(region1 = case_when(region == 2 ~ "South", region == 4 ~ "South", region == 3 ~ "North", TRUE ~ "NA")) %>%
  filter(region1 != "NA") %>% 
  group_by(region1) %>% 
  summarise(mean1 = round(mean(q9worry), 2)) # add round()

ggplot(data=COVIDexplore1, aes(x=region1, y= mean1, fill = region1)) + 
  geom_bar(stat = "identity", width = .5) + 
  scale_y_continuous(limits = c(0,5)) + 
  geom_text(aes(label = mean1), vjust=-0.8, size=5)+
  theme_minimal() + easy_remove_legend_title() + easy_remove_legend() + easy_x_axis_labels_size(10) + easy_y_axis_title_size(12) + easy_x_axis_title_size(12) + labs(x = "Region Divide", y = "Mean Worry", title = "Mean Worry for North vs South") + theme(plot.title = element_text(vjust = 0.5, hjust = 0.5), axis.title.y = element_text(vjust = 2))

# stacked bar plot
COVIDexplore2 <- COVID %>%
  mutate(employment = case_when(Working == 0 ~ "Not Working", Working == 1 ~ "Working", TRUE ~ "NA")) %>%
  filter(employment != "NA") %>%
  group_by(employment, region) %>%
  count()

COVIDexplore2 <- zap_labels(COVIDexplore2) # remove labels

COVIDexplore2$employment <- as.factor(COVIDexplore2$employment)
COVIDexplore2$region <- as.factor(COVIDexplore2$region)
  
ggplot(data=COVIDexplore2, aes(x=region, y=n, fill = employment)) + 
  geom_bar(position = "stack", stat = "identity")
```


