---
title: "Intro to Stats in R"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# load libraries
```{r}
library(palmerpenguins)
library(ggpubr)
library(jmv)
library(rstatix)
library(tidyverse)
library(here)
library(janitor)
library(ggeasy)
library(readxl)
library(gt)
library(haven)
require(gridExtra)
library(gtsummary)

theme_set(theme_bw())
```

# Stats in R using penguins dataset

# Example 1a: Are male penguins heavier than female penguins? (categorical and continuous - 2 groups: male and female)

### descriptive statistics 
```{r}
penguins <- penguins %>%
  na.omit()

body_mass_summary <- penguins %>%
  group_by(sex) %>%
  summarise(mean = mean(body_mass_g), 
            sd = sd(body_mass_g), 
            n = n(), 
            se = sd/sqrt(n))

body_mass_summary %>%
  gt() %>%
  fmt_number(
    columns = 2:5,
    decimals = 2
  )
```

### visualization 
```{r}
# bar plot
body_mass_summary %>%
  ggplot(aes(x = sex, y = mean, fill = sex)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width=.2) +
  scale_y_continuous(expand = c(0,0), limits = c(0,5000)) + # no white space between 0 and x axis
  easy_text_size(15)

# boxplot
plot_1a <- penguins %>%
  na.omit() %>%
  group_by(sex) %>%
  ggplot(aes(x = sex, y = body_mass_g, fill = sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.8) +
  easy_text_size(15)

```

### statistics: we want to compare means between 2 groups... t test
```{r}
female <- penguins %>%
  filter(sex == "female")

male <- penguins %>%
  filter(sex == "male")

t.test(female$body_mass_g, male$body_mass_g)

# or we can use jmv package
ttestIS(formula = body_mass_g ~ sex, data = penguins) # independent samples t test. Dependent variable to the left of ~
```

### ggpubr: "publication ready"
```{r}
plot_1a_pub <- ggboxplot(penguins, x = "sex", y = "body_mass_g",
                color = "sex", palette =c("deepskyblue", "darkred"),
                add = "jitter")

my_comparisons <- list(c("female", "male")) # has to be in a list
plot_1a_pub + 
  stat_compare_means(comparisons = my_comparisons, method="t.test") 
# Add t.test comparisons p-value (if more than 2 groups, you can "anova") 
```

# Example 1b: Do different species have the same or different overall weight? (categorical and continuous - 3 groups)
[https://www.datanovia.com/en/lessons/anova-in-r/](https://www.datanovia.com/en/lessons/anova-in-r/)

### descriptive statistics 
```{r}
penguins <- penguins %>%
  na.omit()

body_mass_summary <- penguins %>%
  group_by(species) %>%
  summarise(mean = mean(body_mass_g), 
            sd = sd(body_mass_g), 
            n = n(), 
            se = sd/sqrt(n))

body_mass_summary %>%
  gt()

penguins %>%
  group_by(species) %>% 
  get_summary_stats(body_mass_g, type = "full")

penguins %>% 
  group_by(species) %>% 
  identify_outliers(body_mass_g)

```

### visualization 
```{r}
# identical code as in example 1a but now species rather than sex

plot_1b <- penguins %>%
  na.omit() %>%
  group_by(species) %>%
  ggplot(aes(x = species, y = body_mass_g, fill = species)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.8) +
  easy_text_size(15)
```

### statistics: we want to compare means between 3 groups... anova
```{r}
# we can still do multiple t tests (but should really use a correction if we do this)
my_comparisons <- list(c("Adelie", "Chinstrap"), c("Chinstrap", "Gentoo")) # has to be in a list
plot_1b + 
  stat_compare_means(comparisons = my_comparisons, method="t.test")

# it's better if we do an anova

# Compute the analysis of variance
aov_1b <- aov(body_mass_g ~ species, data = penguins)
# Summary of the analysis
summary(aov_1b)

# other ways to do anova
# note slightly different results for welch's and fisher's 
# "Welch’s ANOVA isn’t sensitive to unequal variances" https://statisticsbyjim.com/anova/welchs-anova-compared-to-classic-one-way-anova/
anovaOneW(formula = body_mass_g ~ species, data = penguins, fishers = TRUE) # jmv
anova_test(penguins, body_mass_g ~ species) # rstatix
penguins %>% welch_anova_test(body_mass_g ~ species) # rstatix
```


# Example 2: are penguin bills length correlated with flipper length? (continuous and continuous)

### descriptive statistics 
```{r}
penguins %>%
  summarise(across(contains("length"), mean)) %>%
  gt()

```

### visualization 
```{r}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm)) +
  geom_point() +
  geom_smooth(method = "lm") 
```

### statistics: correlation test
```{r}
cor(penguins$bill_length_mm, penguins$flipper_length_mm)

cor.test(penguins$bill_length_mm, penguins$flipper_length_mm)

```

### ggpubr: color by species
```{r}
ggscatter(penguins, x = "bill_length_mm", y = "flipper_length_mm",
          size=1.5,
          add = "reg.line", # Add regression line
          conf.int = TRUE # Add confidence interval
          )

ggscatter(penguins, x = "bill_length_mm", y = "flipper_length_mm",
          size=1.5,
          color = "species",
          shape = "species",
          palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          add = "reg.line", # Add regression line
          conf.int = TRUE # Add confidence interval
          ) +
  stat_cor(aes(color = species), label.x = 30) # Add correlation coefficient (can add this line of code to regular ggplot too!)
```


# Example 3: Do the number of penguin species vary by year? (categorical and categorical)
```{r}
penguins

# descriptive statistics
peng_table <- table(penguins$species, penguins$year)

# visualization
ggplot(penguins, aes(year, ..count..)) +
  geom_bar(aes(fill = species), position = "dodge")
  
# chi squared test
chisq.test(peng_table)
```


# ANOVA
[https://towardsdatascience.com/doing-and-reporting-your-first-anova-and-ancova-in-r-1d820940f2ef](https://towardsdatascience.com/doing-and-reporting-your-first-anova-and-ancova-in-r-1d820940f2ef)
```{r}
penguins

mydata <- iris

# test assumption of homogeneity of variance
library(car)
leveneTest(bill_length_mm~species,penguins) # came back insignificant which is good. This means the variance between bill length and species is not significantly different so we can move forward. does not violate assumption of homogeneity of variance

anova_results = aov(bill_length_mm ~ species, penguins)
summary(anova_results)

library(psych)
describeBy(penguins$bill_length_mm, penguins$species)
```

## Report ANOVA results
We observed differences in bill lengths between the three species of Adelie (M=38.82), Chinstrap (M=48.83), and Gentoo (M=47.57). An ANOVA showed that these differences between species were significant, i.e. there was a significant effect of the species on the bill length of the penguins, F(2,330)=397.3, p<.001.

# ANCOVA
```{r}
ancova_results=aov(bill_length_mm ~ species+sex, penguins) # controlling for body sex

# summary function won't work here
Anova(ancova_results, type="III")
```

## Report ANCOVA results
The covariate, sex, was significantly related to the penguins' bill length, F(1,329)=210.17, p<.001. There was also a significant effect of the species of the penguins on the bill length after controlling for sex, F(2,329)=645.44, p<.001.

# linear regression
lm([target variable] ~ [predictor variables], data = [data source])
```{r}
lm_penguin = lm(bill_length_mm~body_mass_g , data = penguins) #Create the linear regression
summary(lm_penguin)
```
[https://www.statsimprove.com/en/what-is-the-difference-between-anova-and-regression-and-which-one-to-choose/](https://www.statsimprove.com/en/what-is-the-difference-between-anova-and-regression-and-which-one-to-choose/)

# Group 2

- trouble reproducing Study 2 Empathy Physical Distancing plot
```{r}
group2 <- read_excel(here("data", "3_pfattheicher", "Study2.xlsx"))

fig1 <- group2 %>%
  rowid_to_column("ID") %>% 
  select(ID, ve, sd, sdR)

# raw data, this doesn't have any values recoded
ggplot(fig1, aes(x=ve, y=sd)) +
  geom_smooth(method = "lm", colour = "black", se = TRUE) +
  theme_bw() +
  ylim(1,5) +
  labs(title = "Study 2: German Sample", 
       x = "Empathy",
       y = "Social Distance")

# there's actually another variable sdR that already accounts for the reverse coding
ggplot(fig1, aes(x=ve, y=sdR)) +
  geom_smooth(method = "lm", colour = "black", se = TRUE) +
  theme_bw() +
  ylim(1,5) +
  labs(title = "Study 2: German Sample", 
       x = "Empathy",
       y = "Social Distance")
```
