---
title: "Stats Continued"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warnings = FALSE, message = FALSE)
```

```{r}
library(palmerpenguins)
library(tidyverse)
library(janitor)
library(here)
library(rstatix)
library(ggeasy)
library(ggpubr)

library(corrplot)
library(car)
library(psych)
library(BayesFactor)
# remotes::install_github("rasmusab/bayesian_first_aid")
library(BayesianFirstAid)
# devtools::install_github("ropenscilabs/ozbabynames")
library(ozbabynames)
```

# Error Bars

- example with covid data
```{r}
mydat <- read_csv("data/9_folk/Study2.csv") %>% 
  clean_names()

low_extroV <- quantile(mydat$t1extraversion)[2] # lowest quantile for introverts
high_extroV <- quantile(mydat$t1extraversion)[4] # highest quantile for extroverts

fig <- mydat %>%
  select(participant_id, t1lonely, t2lonely, t1extraversion) %>%
  mutate(cat_extraV = ifelse(t1extraversion < low_extroV, "Most Introverted",
                             ifelse(t1extraversion > high_extroV, "Most Extroverted", "neither"))) %>% # create new column where people are categorized as introvert, extravert, or neither
  filter(cat_extraV != "neither") %>% # we only want to have introverts and extroverts
  pivot_longer(cols = t1lonely:t2lonely, names_to = "time") %>%
  group_by(time, cat_extraV) %>%
  get_summary_stats(value, type = "mean_se") # we need to get both the mean and standard error for error bars 

fig$time <- factor(fig$time, labels = c("Before Pandemic", "After Pandemic"))

ggplot(fig, aes(time, mean, group = cat_extraV)) +
  geom_point() +
  geom_line(aes(linetype = cat_extraV)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .1) +
  theme_bw() +
  easy_remove_legend_title()
```

# Correlation Matrix

- back to penguins dataset
```{r}
penguins <- penguins %>%
  na.omit()

peng_corr <- penguins %>%
  select(bill_length_mm:body_mass_g) %>%
  cor()

corrplot(peng_corr, type = "upper")

corrplot(peng_corr, type = "upper", method = "ellipse")

corrplot(peng_corr, type = "upper", method = "number")

```


# ANOVA vs ANCOVA vs Linear Regression

- let's imagine we have 1 continuous DV, whether we want to use ANOVA or Linear Regression depends on the type of predictors
- Linear Regression = if predictors are all continuous 
- ANOVA = if predictors are all categorical 
- ANCOVA = if you have both categorical and continuous predictors 
- *these are all linear models - thanks to Danielle for confirming this is right*
- *these models make several assumptions about the data - good to check first*

- [Linear Models](https://lindeloev.github.io/tests-as-linear/) <br>
- [ANOVA and ANCOVA in R](https://towardsdatascience.com/doing-and-reporting-your-first-anova-and-ancova-in-r-1d820940f2ef) <br>
- [Linear Regression](https://www.datacamp.com/community/tutorials/linear-regression-R)<br>
- [ANOVA assumptions](https://www.datanovia.com/en/lessons/anova-in-r/)

# Linear Regression 

- y = mx + b
- DV: body mass and predictor variables: bill length and flipper length 
- lm([dependent variable] ~ [predictor variables], data = [data source])
```{r}
# main effects model
lm_penguins <- lm(body_mass_g ~ bill_length_mm + flipper_length_mm, penguins)
summary(lm_penguins)

# main effects + interaction model
lm2_penguins <- lm(body_mass_g ~ bill_length_mm * flipper_length_mm, penguins)
summary(lm2_penguins)
```
- Call = model 
- residuals = difference between observed and predicted values
- coefficients = intercept + predictor variables 
- residual standard error = sd of the residuals
- R^2 = what % of the variance can be explained by the regression

## Report linear regression
A linear regression was calculated to predict body mass based on bill and flipper length. There is a significant main effect of bill length and a significant interaction between bill length and flipper length (p < 0.001). A significant regression equation was found (F(3, 329) = 370.1, p < 0.001) with an R^2 of 0.77. 

# ANOVA

- DV: bill length and predictor variable: species 
- aov([dependent variable] ~ [predictor variables], data = [data source])
```{r}
anova_results <- aov(bill_length_mm ~ species, penguins)
summary(anova_results)

# psych package

describeBy(penguins$bill_length_mm, penguins$species)
```

## Report ANOVA results
We observed differences in bill lengths between the three species of Adelie (M=38.82), Chinstrap (M=48.83), and Gentoo (M=47.57). An ANOVA showed that these differences between species were significant, i.e. there was a significant effect of the species on the bill length of the penguins, F(2,330)=397.3, p<.001.

# ANCOVA

- DV: bill length and predictor variables: species and body mass
```{r} 
ancova_results <- aov(bill_length_mm ~ species + body_mass_g, penguins)

Anova(ancova_results, type = "III") # specifies type III errors, whereas summary() defaults to Type I errors (not a problem when performing a simple ANOVA) 
# see ANOVA and ANCOVA in R link for further explanation
 
```

## Report ANCOVA results
The covariate, body mass, was significantly related to the penguins' bill length, F(1,329)=168.76, p<.001. There was also a significant effect of the species of the penguins on the bill length after controlling for body mass, F(2,329)=388.95, p<.001.


# ANOVA is directly related to the linear model so let's compare aov() and lm()
- DV: body mass and predictor variables: bill length and flipper length
```{r}
AOV <- aov(body_mass_g ~ bill_length_mm + flipper_length_mm, penguins)
summary(AOV)

LM <- lm(body_mass_g ~ bill_length_mm + flipper_length_mm, penguins)
anova(LM)
summary(LM)
```

# how to test if model is a good fit?
- look at R^2, usually a higher R^2 is a better fit (but only if you're assuming your data should fit a linear line)
- Multiple R^2 will always increase if you include additional variables, that is why it's better to look at the adjusted R^2

# Example to understand R^2

- body mass and bill length
- body mass and flipper length
```{r}
gentoo_f_penguins <- penguins %>%
  filter(sex == "female" & species == "Gentoo")

ggplot(gentoo_f_penguins, aes(body_mass_g, bill_length_mm)) +
  geom_jitter() +
  geom_smooth(method = "lm") +
  theme_bw() +
  stat_regline_equation(aes(label = ..adj.rr.label..))

ggplot(gentoo_f_penguins, aes(body_mass_g, flipper_length_mm)) +
  geom_jitter() +
  geom_smooth(method = "lm") +
  theme_bw() +
  stat_regline_equation(aes(label = ..adj.rr.label..))

```


# bayesian stats

- takes prior knowledge into account 

Example from stack overflow:
I have misplaced my phone somewhere in the home. I can use the phone locator on the base of the instrument to locate the phone and when I press the phone locator the phone starts beeping.

Problem: Which area of my home should I search?

**Frequentist Reasoning**
I can hear the phone beeping. I also have a mental model which helps me identify the area from which the sound is coming. Therefore, upon hearing the beep, I infer the area of my home I must search to locate the phone.

**Bayesian Reasoning**
I can hear the phone beeping. Now, apart from a mental model which helps me identify the area from which the sound is coming from, I also know the locations where I have misplaced the phone in the past. So, I combine my inferences using the beeps and my prior information about the locations I have misplaced the phone in the past to identify an area I must search to locate the phone.
```{r}
#devtools::install_github("rasmusab/bayesian_first_aid", force = TRUE)
female <- penguins %>%
  filter(sex == "female")

male <- penguins %>%
  filter(sex == "male")

t.test(female$body_mass_g, male$body_mass_g)

# BayesFactor 
ttestBF(female$body_mass_g, male$body_mass_g)

# BayesianFirstAid
# fit <- bayes.t.test(female$body_mass_g, male$body_mass_g)
# plot(fit)
```

# Troubleshooting

## Problem: create a plot with text labels 
```{r}
# devtools::install_github("ropenscilabs/ozbabynames")

ozbabynames

babynames <- ozbabynames %>%
  filter(year == 2017 &
           state == "New South Wales" &
           count > 300)

ggplot(babynames, aes(name, count)) +
  geom_jitter() + 
  facet_wrap(~sex) +
  theme_bw()


```

## goal: add text labels to the plot, so each point is a name rather than a point or in addition to the point

- See what you can come up with and share your plots on Slack!
- We'll pick up here next week
