---
title: "Replicating the Effects of Auditory Religious Cues on Dishonest Behavior"
author: "Martin Lang & Aaron Nichols; Created with R3.5.3"
date: "05/11/2020"
output:
  html_document:
    code_folding: show
    theme: spacelab
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---


<style>

table, th, td {
  border: none;
  padding-left: 0em;
  padding-right: 0em;
  min-width: 110%;
  
}

</style>

## 1. Introduction
This file accompanies manuscript by Nichols et al. titled "Replicating the Effects of Auditory Religious Cues on Dishonest Behavior", which investigate the effects of religious audiorty cues on dishonest behavior. The present file documents statistical analyses reported in the main text and supplementary materials.

## 2.0 Data set up

```{r results='hide', message=FALSE, warning=FALSE, echo=T}

{
###############################################################
### General set up ###
  
# Load libraries
libs <- c("yarrr","dplyr","psych", "glmmADMB", "lsmeans", "nlme", "stargazer")
lapply(libs, require, character.only = TRUE)
# if those packages are not installed, uncomment the line below:
# install.packages(libs)

## Note that glmmADMB may not install using this method. Here is is a code to install glmmADMB 

#install.packages("R2admb")
#install.packages("glmmADMB", 
#    repos=c("http://glmmadmb.r-forge.r-project.org/repos",
#            getOption("repos")),
#    type="source") 


####################################################################################  
## Load data
dA<-read.csv("nichols/Nichols_et_al_dataset_V2.0.csv", stringsAsFactors=FALSE)

# check missing values
dA[sapply(dA, function(dA) any(is.na(dA)))]

# Center & factor variables
dat <- dA %>% 
  mutate(id = as.factor(id),
         age.c = age - mean(age, na.rm=T),
         sex = as.factor(sex),
         relig = abs(relig-5), # reverse coding
         ritual = abs(ritual - 7), # reverse coding
         affil = as.factor(affil_cong), # factor religious affiliation (yes/no)
         impact = (deep + powerful)/2, # as per Lang et al. 2016
         tempo = (fast + abs(slow-7))/2,  # as per Lang et al. 2016
         positivity = (interesting + pleasant + exciting + relaxing + happy)/5,  # as per Lang et al. 2016
         negativity = (distressing + irritating + boring + sad)/4, # as per Lang et al. 2016
         difficult = abs(difficult_task-6),
         CTdiff = CT - CT_cheat,
         claim.b = (claim*459 + 0.5)/460,
         claim = claim*100
         ) %>%
  as_tibble()

dat %>%
  select(id, con)

# Re-order conditions to: religous, secular, noise, and control
dat$con[dat$con==4] <- 0 # make religious prime the reference category
dat$con[dat$con==1] <- 4
dat$con[dat$con==3] <- 1
dat$con[dat$con==4] <- 3

# treatment variable
dat$con<-factor(dat$con,levels= c(0,1,2,3),
                  labels = c("Religious", "Secular", "Noise","Control"))


# site variable - USA is the reference category
dat$sit <- dat$site
dat$site<-factor(dat$site,levels= c(1,2,3),
                 labels = c("USA", "CZ","JP"))


## Exclude PPTs ###########################################################################
# Exclude participants who guessed the hypotheses and played the game before
dat.full <- dat
dat <- dat[dat$include!=1,]

# Create site subsamples
USA <- dat[dat$site=="USA",]
CZ <- dat[dat$site=="CZ",]
JP <- dat[dat$site=="JP",]
sites <- c("USA", "CZ", "JP")
}
```

### 2.1. Histograms

Histogram of percentage of money claimed dishonestly


```{r results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.height=5, fig.width=6}

par(mfrow=c(1,1))
hist(dat$claim, breaks = seq(0,100,5), freq = F,xlab = 'Claim', ylab = 'Probability',
     main = 'Histogram with Normal PDF',col="grey78", border="deepskyblue1", lty=1,
     ylim=c(0,0.05),xlim=c(0,100))
```

Histograms of claim per site


```{r results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.height=6, fig.width=10}

par(mfrow=c(1,3))
  for (i in 1:3){
    sit = eval(parse(text = sites[i]))
    hist(sit$claim, breaks = seq(0,100,5), freq = F,
         main = parse(text = sites[i]), col="grey78", border="deepskyblue1",
         lty=1, ylim=c(0,0.1))}

```


### 2.2. Distributions of main variables

Pirate plots of various variables by site these plots combine scatter plots (dots), density function (beans), and mean with 95% confidence interval (bar with a box). We recommend to zoom in the result to see the details.
These four plots show between-site differences in the percentage of money claimed, age, religiousness, and the frequency of ritual behavior.

```{r results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.height=9, fig.width=9}

{par(mfrow=c(2,2))
{pirateplot(formula = claim ~ site,
           data = dat,
           theme = 0,
           main = "",
           pal = "basel", # southpark color palette
           bean.b.o = 1, # Bean fill
           bean.f.o = .005, # Bean fill
           point.o = .7, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .96, # Inference border
           avg.line.o = 1, # Aver line
           bar.f.o = .2, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           point.pch = 21,
           point.bg = "white",
           point.cex = 1,
           point.lwd = 2,
           bean.lwd = 2)}

  
{pirateplot(formula = age ~ site,
            data = dat,
            theme = 0,
            main = "",
            pal = "basel", # southpark color palette
            bean.b.o = 1, # Bean fill
            bean.f.o = .005, # Bean fill
            point.o = .7, # Points
            inf.f.o = .7, # Inference fill
            inf.b.o = .96, # Inference border
            avg.line.o = 1, # Aver line
            bar.f.o = .2, # Bar
            inf.f.col = "white", # Inf fill col
            inf.b.col = "black", # Inf border col
            avg.line.col = "black", # avg line col
            point.pch = 21,
            point.bg = "white",
            point.cex = 1,
            point.lwd = 2,
            bean.lwd = 2)}

{pirateplot(formula = relig ~ site,
            data = dat,
            theme = 0,
            main = "",
            pal = "basel", # southpark color palette
            bean.b.o = 1, # Bean fill
            bean.f.o = .005, # Bean fill
            point.o = .7, # Points
            inf.f.o = .7, # Inference fill
            inf.b.o = .96, # Inference border
            avg.line.o = 1, # Aver line
            bar.f.o = .2, # Bar
            inf.f.col = "white", # Inf fill col
            inf.b.col = "black", # Inf border col
            avg.line.col = "black", # avg line col
            point.pch = 21,
            point.bg = "white",
            point.cex = 1,
            point.lwd = 2,
            bean.lwd = 2)}

{pirateplot(formula = ritual ~ site,
            data = dat,
            theme = 0,
            main = "",
            pal = "basel", # southpark color palette
            bean.b.o = 1, # Bean fill
            bean.f.o = .005, # Bean fill
            point.o = .7, # Points
            inf.f.o = .7, # Inference fill
            inf.b.o = .96, # Inference border
            avg.line.o = 1, # Aver line
            bar.f.o = .2, # Bar
            inf.f.col = "white", # Inf fill col
            inf.b.col = "black", # Inf border col
            avg.line.col = "black", # avg line col
            point.pch = 21,
            point.bg = "white",
            point.cex = 1,
            point.lwd = 2,
            bean.lwd = 2)}}
```

Pirate plots of the same variables by condition


```{r results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.height=9, fig.width=9}

{par(mfrow=c(2,2))
  {pirateplot(formula = claim ~ con,
              data = dat,
              theme = 0,
              main = "",
              pal = "basel", # southpark color palette
              bean.b.o = 1, # Bean fill
              bean.f.o = .005, # Bean fill
              point.o = .7, # Points
              inf.f.o = .7, # Inference fill
              inf.b.o = .96, # Inference border
              avg.line.o = 1, # Aver line
              bar.f.o = .2, # Bar
              inf.f.col = "white", # Inf fill col
              inf.b.col = "black", # Inf border col
              avg.line.col = "black", # avg line col
              point.pch = 21,
              point.bg = "white",
              point.cex = 1,
              point.lwd = 2,
              bean.lwd = 2)}
  
  {pirateplot(formula = age ~ con,
              data = dat,
              theme = 0,
              main = "",
              pal = "basel", # southpark color palette
              bean.b.o = 1, # Bean fill
              bean.f.o = .005, # Bean fill
              point.o = .7, # Points
              inf.f.o = .7, # Inference fill
              inf.b.o = .96, # Inference border
              avg.line.o = 1, # Aver line
              bar.f.o = .2, # Bar
              inf.f.col = "white", # Inf fill col
              inf.b.col = "black", # Inf border col
              avg.line.col = "black", # avg line col
              point.pch = 21,
              point.bg = "white",
              point.cex = 1,
              point.lwd = 2,
              bean.lwd = 2)}
  
  {pirateplot(formula = relig ~ con,
              data = dat,
              theme = 0,
              main = "",
              pal = "basel", # southpark color palette
              bean.b.o = 1, # Bean fill
              bean.f.o = .005, # Bean fill
              point.o = .7, # Points
              inf.f.o = .7, # Inference fill
              inf.b.o = .96, # Inference border
              avg.line.o = 1, # Aver line
              bar.f.o = .2, # Bar
              inf.f.col = "white", # Inf fill col
              inf.b.col = "black", # Inf border col
              avg.line.col = "black", # avg line col
              point.pch = 21,
              point.bg = "white",
              point.cex = 1,
              point.lwd = 2,
              bean.lwd = 2)}
  
  {pirateplot(formula = ritual ~ con,
              data = dat,
              theme = 0,
              main = "",
              pal = "basel", # southpark color palette
              bean.b.o = 1, # Bean fill
              bean.f.o = .005, # Bean fill
              point.o = .7, # Points
              inf.f.o = .7, # Inference fill
              inf.b.o = .96, # Inference border
              avg.line.o = 1, # Aver line
              bar.f.o = .2, # Bar
              inf.f.col = "white", # Inf fill col
              inf.b.col = "black", # Inf border col
              avg.line.col = "black", # avg line col
              point.pch = 21,
              point.bg = "white",
              point.cex = 1,
              point.lwd = 2,
              bean.lwd = 2)}}


```


Assess task difficulty across sites. First two plots show data for completion times during cheating trials and difficulty for full data set. The second row limits data span only to participants who cheated in less than 20% of the cases. One Czech outlier removed from the completion times.

```{r results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.height=9, fig.width=9}

{par(mfrow=c(3,2))
  {pirateplot(formula = CT ~ site,
           data = dat[dat$CT_cheat < 14,],
           theme = 0,
           main = "",
           pal = "basel", # southpark color palette
           bean.b.o = 1, # Bean fill
           bean.f.o = .005, # Bean fill
           point.o = .7, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .96, # Inference border
           avg.line.o = 1, # Aver line
           bar.f.o = .2, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           point.pch = 21,
           point.bg = "white",
           point.cex = 1,
           point.lwd = 2,
           bean.lwd = 2)}

  {pirateplot(formula = difficult ~ site,
           data = dat[dat$CT_cheat < 14,],
           theme = 0,
           main = "",
           pal = "basel", # southpark color palette
           bean.b.o = 1, # Bean fill
           bean.f.o = .005, # Bean fill
           point.o = .7, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .96, # Inference border
           avg.line.o = 1, # Aver line
           bar.f.o = .2, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           point.pch = 21,
           point.bg = "white",
           point.cex = 1,
           point.lwd = 2,
           bean.lwd = 2)}
  
  {pirateplot(formula = CT ~ site,
           data = dat[dat$claim < 20 & dat$CT_cheat < 14,],
           theme = 0,
           main = "",
           pal = "basel", # southpark color palette
           bean.b.o = 1, # Bean fill
           bean.f.o = .005, # Bean fill
           point.o = .7, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .96, # Inference border
           avg.line.o = 1, # Aver line
           bar.f.o = .2, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           point.pch = 21,
           point.bg = "white",
           point.cex = 1,
           point.lwd = 2,
           bean.lwd = 2)}

  {pirateplot(formula = difficult ~ site,
           data = dat[dat$claim < 20 & dat$CT_cheat < 14,],
           theme = 0,
           main = "",
           pal = "basel", # southpark color palette
           bean.b.o = 1, # Bean fill
           bean.f.o = .005, # Bean fill
           point.o = .7, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .96, # Inference border
           avg.line.o = 1, # Aver line
           bar.f.o = .2, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           point.pch = 21,
           point.bg = "white",
           point.cex = 1,
           point.lwd = 2,
           bean.lwd = 2)}}
  


  
```

### 2.3. Means and SD

```{r results='show', message=FALSE, warning=FALSE, echo=T, cache = F}
## Report means and SD ###########################################################################
# THis approach is fof the sacred variable. You can just replce the word "sacred" 
# with e.g. "claim" to get all the same parameters for the claim variable
{
# Religious condition
mean0 <- mean(dat$claim[dat$con=="Religious"], na.rm = T) # mean
sd0 <- sd(dat$claim[dat$con=="Religious"], na.rm = T) # standard deviation
n0 <- length(dat$con[dat$con=="Religious" & !is.na(dat$con)]) # number of observations
se0 <- sd0/sqrt(n0) # standard error
lCI0 <- mean0 - (1.96*se0) # lower 95% CI
uCI0 <- mean0 + (1.96*se0) # upper 95% Ci

# Secular condition
mean1 <- mean(dat$claim[dat$con=="Secular"], na.rm = T) # mean
sd1 <- sd(dat$claim[dat$con=="Secular"], na.rm = T) # standard deviation
n1 <- length(dat$con[dat$con=="Secular" & !is.na(dat$con)]) # number of observations
se1 <- sd1/sqrt(n1) # standard error
lCI1 <- mean1 - (1.96*se1) # lower 95% CI
uCI1 <- mean1 + (1.96*se1) # upper 95% Ci

# Noise condition
mean2 <- mean(dat$claim[dat$con=="Noise"], na.rm = T) # mean
sd2 <- sd(dat$claim[dat$con=="Noise"], na.rm = T) # standard deviation
n2 <- length(dat$con[dat$con=="Noise" & !is.na(dat$con)]) # number of observations
se2 <- sd2/sqrt(n2) # standard error
lCI2 <- mean2 - (1.96*se2) # lower 95% CI
uCI2 <- mean2 + (1.96*se2) # upper 95% Ci

# Control condition
mean3 <- mean(dat$claim[dat$con=="Control"], na.rm = T) # mean
sd3 <- sd(dat$claim[dat$con=="Control"], na.rm = T) # standard deviation
n3 <- length(dat$con[dat$con=="Control" & !is.na(dat$con)]) # number of observations
se3 <- sd3/sqrt(n3) # standard error
lCI3 <- mean3 - (1.96*se3) # lower 95% CI
uCI3 <- mean3 + (1.96*se3) # upper 95% Ci

# compute Cohen's d

# Relig vs. Secular
d1 <- (mean0-mean1)/sqrt((sd0^2+sd1^2)/2)
# Relig vs. Noise
d2 <- (mean0-mean2)/sqrt((sd0^2+sd2^2)/2)
# Relig vs. Control
d3 <- (mean0-mean3)/sqrt((sd0^2+sd3^2)/2)
}

# Display the results for your table 1
# number of participants; mean value; standard deviation; 95% CI; and Cohen's d
rel <- c(n0,mean0,sd0,lCI0,uCI0)
sec <- c(n1,mean1,sd1,lCI1,uCI1,d1)
noi <- c(n2,mean2,sd2,lCI2,uCI2,d2)
con <- c(n3,mean3,sd3,lCI3,uCI3,d3)

print(rez <- as.data.frame(cbind(rel,sec,noi,con)), digits = 2)


print(dat %>% group_by(site) %>% summarise(M = mean(age, na.rm = T), SD = sd(age, na.rm = T), NROW(id)))

print(dat %>% group_by(site) %>% summarise(M = mean(claim, na.rm = T), SD = sd(claim, na.rm = T), NROW(id)))

```

## 3.0 Main models


We approached the modeling of our dependent variable quite simply: while we could have used linear mixed-models (LMM) with site as the nesting factor, or generalized linear models (GLMs) accounting for the bounded nature of our data, we opted for simplicity and intepretability. So, we proceed with ordinary least squares models with the religious condition as a  reference category (all, other conditions are compared to it) and the USA as the reference site (this choice was arbitrary, we are not really interested in the differences across sites). However, we also report Beta regression, which are appropriate for percentage data. Nevertheless, the results are qualitatively similar.


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}
# Maniuplation check
summary(lm0 <- lm(sacred ~ con, data = dat))

summary(lm0.1 <- lm(religious ~ con, data = dat))
```
```{r echo=FALSE, results='asis'}
stargazer(lm0,lm0.1, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

# First, simple condition effect holding site intercepts constant (no effect in the original study)
summary(lm1 <- lm(claim ~ con + sex + age.c + site, data = dat))

# Add interaction with religiosity (significant in the original study)
summary(lm2 <- lm(claim ~ con*relig + sex + age.c + site, data=dat))

# Add interaction with ritual frequency (trending in the original study)
summary(lm3 <- lm(claim ~ con*ritual + sex + age.c + site, data=dat))

# Add interaction with affiliation to the religion associated with our religious prime (not explored in the original study)
summary(lm4 <- lm(claim ~ con*affil + sex + age.c + site, data = dat))

```

```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3,lm4, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```



Model diagnostics

```{r message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow=c(3,1), mar=c(2,2,2,2))
plot(predict(lm4), lm4$residuals,  main = "Fitted vs Residuals")
qqnorm(lm4$residuals, main = "QQ plot")
hist(lm4$residuals, main = "Histogram")
```




## 4.0 Supplementary Material


### 4.1 Musical ratings

```{r results='show', message=FALSE, warning=FALSE, echo=T, cache = F}
# Maniuplation check
summary(lm1 <- lm(positivity ~ con, data = dat))
lsmeans(lm1, pairwise~con)

summary(lm2 <- lm(negativity ~ con, data = dat))
lsmeans(lm2, pairwise~con)

summary(lm3 <- lm(tempo ~ con, data = dat))
lsmeans(lm3, pairwise~con)

summary(lm4 <- lm(impact ~ con, data = dat))
lsmeans(lm4, pairwise~con)

```


### 4.2 Site-specific models

In this section, we replicate the site-specific models from Lang et al. (2016) and add site-specific models also for the other moderating variables.


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

# USA
summary(lm1 <- lm(claim ~ con*relig + sex + age.c, data=USA))

# CZ
summary(lm2 <- lm(claim ~ con*relig + sex + age.c, data=CZ))

# JP
summary(lm3 <- lm(claim ~ con*relig + sex + age.c, data=JP))

```

```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

# USA
summary(lm1 <- lm(claim ~ con*ritual + sex + age.c, data=USA))

# CZ
summary(lm2 <- lm(claim ~ con*ritual + sex + age.c, data=CZ))

# JP
summary(lm3 <- lm(claim ~ con*ritual + sex + age.c, data=JP))

```

```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

# USA
summary(lm1 <- lm(claim ~ con*affil + sex + age.c, data=USA))

# CZ
summary(lm2 <- lm(claim ~ con*affil + sex + age.c, data=CZ))

# JP
summary(lm3 <- lm(claim ~ con*affil + sex + age.c, data=JP))

```

```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


### 4.3 Beta regression

```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}
# transform data to accomodate them for the need of the Beta regression (Smithson & Verkulien, 2006)

# create separata data sets, exluding missing values pairwise
dat1 <- na.omit(subset(dat, select = c(claim.b, con, relig, sex, age.c, site)))
dat2 <- na.omit(subset(dat, select = c(claim.b, con, ritual, sex, age.c, site)))
dat3 <- na.omit(subset(dat, select = c(claim.b, con, affil, sex, age.c, site)))


summary(glm1 <- glmmadmb(claim.b ~ con*relig + sex + age.c + site, family = 'beta', data=dat1))
summary(glm2 <- glmmadmb(claim.b ~ con*ritual + sex + age.c + site, family = 'beta', data=dat2))
summary(glm3 <- glmmadmb(claim.b ~ con*affil + sex + age.c + site, family = 'beta', data=dat3))



cf <- summary(glm1)$coefficients[,1]
se <- sqrt(diag(vcov(glm1)))
p <- summary(glm1)$coefficients[,4]
ci <- (cbind(est = (plogis(cf)-0.5), LL = (plogis(cf - 1.96 * se)-0.5),
             UL = (plogis(cf + 1.96 * se)-0.5),p))
ci[1,] <- (ci[1,]+0.5)
ci1 <- ci

cf <- summary(glm2)$coefficients[,1]
se <- sqrt(diag(vcov(glm2)))
p <- summary(glm2)$coefficients[,4]
ci <- (cbind(est = (plogis(cf)-0.5), LL = (plogis(cf - 1.96 * se)-0.5),
             UL = (plogis(cf + 1.96 * se)-0.5),p))
ci[1,] <- (ci[1,]+0.5)
ci2 <- ci

cf <- summary(glm3)$coefficients[,1]
se <- sqrt(diag(vcov(glm3)))
p <- summary(glm3)$coefficients[,4]
ci <- (cbind(est = (plogis(cf)-0.5), LL = (plogis(cf - 1.96 * se)-0.5),
             UL = (plogis(cf + 1.96 * se)-0.5),p))
ci[1,] <- (ci[1,]+0.5)
ci3 <- ci

```
```{r echo=FALSE, results='asis'}
stargazer(ci1,ci2,ci3, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = "", notes.append = F, ci = T, type = "html", digits = 2)

```



### 4.4 Linear mixed models

```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

summary(lm1 <- lme(claim ~ con*relig + sex + age.c, random = ~1|site, data = dat, na.action = na.omit))

summary(lm2 <- lme(claim ~ con*ritual + sex + age.c, random = ~1|site, data = dat, na.action = na.omit))

summary(lm3 <- lme(claim ~ con*affil + sex + age.c, random = ~1|site, data = dat, na.action = na.omit))

```
```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


### 4.5 Adding control variables


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}

summary(lmx <- lm(difficult~site + age.c + sex, data = dat))
lsmeans(lmx, pairwise~site)


# Add interaction with religiosity (significant in the original study)
summary(lm1 <- lm(claim ~ con*relig + sex + age.c + difficult + CTdiff + site, data=dat))
summary(lm2 <- lm(claim ~ con*relig + sex + age.c + impact + tempo + positivity + negativity + difficult + CTdiff + site, data=dat))

# Add interaction with ritual frequency (trending in the original study)
summary(lm3 <- lm(claim ~ con*ritual + sex + age.c + difficult + CTdiff+ site, data=dat))
summary(lm4 <- lm(claim ~ con*ritual + sex + age.c + impact + tempo + positivity + negativity + difficult + CTdiff + site, data=dat))

# Add interaction with affiliation to the religion associated with our religious prime (not explored in the original study)
summary(lm5 <- lm(claim ~ con*affil + sex + age.c + difficult + CTdiff + site, data=dat))
summary(lm6 <- lm(claim ~ con*affil + sex + age.c + impact + tempo + positivity + negativity + difficult + CTdiff + site, data=dat))

```
```{r echo=FALSE, results='asis'}
stargazer(lm1,lm2,lm3,lm4,lm5,lm6, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```


### 4.6 Full-data models


```{r results='hide', message=FALSE, warning=FALSE, echo=T, cache = F}
# First, explore the differences in the incorrectly claimed higher-paying sides between the excluded and included particiapants

summary(lm1 <- lm(claim ~ include + sex + age.c + site, data=dat.full))

## look only at 100% incorrect claims
dat.full$claim.bin <- dat.full$claim
dat.full$claim.bin[dat.full$claim.bin < 100] <- 0
dat.full$claim.bin[dat.full$claim.bin == 100] <- 1

summary(lm2 <- glm(claim.bin ~ include + sex + age.c + site, data=dat.full, family = "binomial"))
exp(lm2$coefficients[2])


# run basic models on full sample

summary(lm3 <- lm(claim ~ con + sex + age.c + site, data = dat.full))

summary(lm4 <- lm(claim ~ con*relig + sex + age.c + site, data=dat.full))

summary(lm5 <- lm(claim ~ con*ritual + sex + age.c + site, data=dat.full))

summary(lm6 <- lm(claim ~ con*affil + sex + age.c + site, data=dat.full))



```
```{r echo=FALSE, results='asis'}
stargazer(lm3,lm4,lm5,lm6, title="Estimates with 95% CI",  multicolumn = F, df = F, header=FALSE, omit.stat = c("ll","wald","AIC","BIC","adj.rsq","rsq","f","ser"), dep.var.caption  = "",no.space = F,  p.auto = FALSE, star.char = c("x", "*", "**","***"),  star.cutoffs = c(0.1, 0.05, 0.01, 0.001), notes = c("x p<.1; * p<.05; ** p<.01; *** p<.001"), notes.append = F, ci = T, type = "html", digits = 2)

```