---
title: "brick"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(PupillometryR)
library(ggeasy)
```

- use merged.rda file as the merged.csv was a massive file
```{r}
#brick_raw <- read_csv(here("brick", "merged.csv"))
load(file = "brick/merged.rda")

prolific <- merged %>%
  clean_names() %>%
  filter(study == "Prolific")
n_prolific = length(unique(prolific$id))

length(unique(prolific$id))

mturk <- merged %>%
  clean_names() %>%
  filter(study == "MTurk")
n_mturk = length(unique(mturk$id))
```

# demographics: Prolific
```{r}
prolific_dem <- prolific %>%
  select(id, age, female) 

describe(prolific_dem) # age mean, min, max

prolific_dem %>%
  group_by(female) %>%
  count()


tabyl(prolific_dem$female)

prolific_dem %>%
  filter(female == 1 | female == 2) %>%
  tabyl(female)

```

# demographics: MTurk 
```{r}
mturk_dem <- mturk %>%
  select(id, age, female) 

describe(mturk_dem) # age mean, min, max

mturk_dem %>%
  group_by(female) %>%
  count()


tabyl(mturk_dem$female)

mturk_dem %>%
  filter(female == 1 | female == 2) %>%
  tabyl(female)

```

# table 4
```{r}
# only values = 1
table4_P <- prolific %>%
  select(id,study, blood_paid_self, blood_unpaid_self, blood_paid_others, blood_unpaid_others) %>%
  na.omit()

tabyl(table4_P$blood_paid_self)
tabyl(table4_P$blood_unpaid_self)

mean(table4_P$blood_paid_others)
sd(table4_P$blood_paid_others)

mean(table4_P$blood_unpaid_others)
sd(table4_P$blood_unpaid_others)

table4_M <- mturk %>%
  select(id,study, blood_paid_self, blood_unpaid_self, blood_paid_others, blood_unpaid_others) %>%
  na.omit()

tabyl(table4_M$blood_paid_self)
tabyl(table4_M$blood_unpaid_self)

mean(table4_M$blood_paid_others)
sd(table4_M$blood_paid_others)

mean(table4_M$blood_unpaid_others)
sd(table4_M$blood_unpaid_others)
```

# table 5
- overestimation: mean difference of estimates between paid and unpaid conditions and subtracting the mean difference between paid and unpaid conditions of self reported willingness
```{r}
# difference in self donation between payment conditions was 76.8-71.2 = 5.6%

merged <- merged %>%
  mutate(overestimation_S1 = self_interest_others_S1 - 5.6)
merged$overestimation_S1[is.na(merged$self_interest_others_S1)] <- NA

# mean(merged$overestimation_S1, na.rm = TRUE)
# sd(merged$overestimation_S1, na.rm = TRUE)

overest_M <- merged %>%
  filter(study == "MTurk") %>%
  select(id, overestimation_S1) %>%
  na.omit()
mean(overest_M$overestimation_S1, na.rm = TRUE)
sd(overest_M$overestimation_S1, na.rm = TRUE)

overest_P <- merged %>%
  filter(study == "Prolific") %>%
  select(id, overestimation_S1) %>%
  na.omit()
mean(overest_P$overestimation_S1, na.rm = TRUE)
sd(overest_P$overestimation_S1, na.rm = TRUE)

```


# figure 1 
- haven't tried to add the boxplot below but I believe you can position the histogram up and pretty easily add the boxplot below
```{r}
fig1 <- merged %>%
  select(id, donation_payment_others, estimate_S1) %>%
  na.omit()

ggplot(fig1, aes(donation_payment_others, estimate_S1, fill = donation_payment_others)) +
  geom_flat_violin() +
  coord_flip() +
  theme_classic() +
  labs(y = "Estimated donation in others (%)", x = "") +
  easy_remove_legend()



```

# figure 2
- ...this doesn't look right but I didn't think it was super clear what the histograms were plotting
```{r}
fig2 <- merged %>%
  filter(study == "MTurk") %>%
  select(id, policy_self, overestimation_S1)%>%
  filter(policy_self == 1) %>%
  distinct() %>%
  na.omit()

ggplot(fig2, aes(overestimation_S1)) +
  geom_histogram(bins = 20)

```

# Study 4 - haven't looked at yet