---
title: "harris"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(haven)
library(psych)
library(ggpubr)
library(ggeasy)
```

```{r}
humiston_raw <- read_sav(here("humiston", "Humiston & Wamsley 2019 data.sav"))

humiston <- humiston_raw %>%
  clean_names() %>%
  filter(general_1_race == 1)
  

```

# demographics
- not clear what exclusions already exist in the raw data
- filtering race gets n=31
- there is an exclude and filter column though
```{r}
demo <- humiston %>%
  select(participant_id, general_1_age:demo_1_non_participat) %>%
  filter(general_1_race == 1)

length(unique(demo$participant_id))

age_sex <- demo %>%
  select(general_1_age, general_1_sex)

describe(age_sex$general_1_age)

age_sex %>%
  group_by(general_1_sex) %>%
  count()

```

# Table 1
- ESS = epworth_total for epworth sleeping scale
- SSS = not sure, need to read the paper more closely
- didn't finish, but this doesn't look too hard
```{r}
glimpse(humiston)
table1 <- humiston %>%
  select(participant_id, general_1_age, general_1_race, epworth_total, total_sleep)

describe(table1$epworth_total)

length(unique(table1$participant_id))
```


# Table 2
- race and gender implicit bias levels
```{r}
table2 <- humiston %>%
  select(participant_id, base_iat_race, base_iat_gen, pre_iat_race, pre_iat_gen, post_iat_race, post_iat_gen)

describe(table2)

```

# Figure 3
- first attempt... doesn't look right, definitely wrong values for 1 week
```{r}
fig3_summary <- humiston %>%
  select(participant_id, base_ia_tcued, base_ia_tuncued, pre_ia_tcued, pre_ia_tuncued, post_ia_tcued, post_ia_tuncued, week_ia_tcued, week_ia_tuncued) %>%
  pivot_longer(base_ia_tcued:week_ia_tuncued) %>%
  mutate(cond = case_when((name == "base_ia_tcued" | name == "base_ia_tuncued") ~ "Baseline",
    (name == "pre_ia_tcued" | name == "pre_ia_tuncued") ~ "Prenap",
    (name == "post_ia_tcued" | name == "post_ia_tuncued") ~ "Postnap",
    (name == "week_ia_tcued" | name == "week_ia_tuncued") ~ "1-Week",
    (name == "week_ia_tcued" | name == "week_ia_tuncued") ~ "Postnap")) %>%
  mutate(cued = ifelse(name %in% c("base_ia_tcued", "pre_ia_tcued", "post_ia_tcued", "week_ia_tcued"), "Cued", "Uncued")) %>%
  group_by(cond, cued) %>%
  summarise(mean = mean(value), 
            sd = sd(value), 
            n = n(), 
            se = sd/sqrt(n))

fig3_summary$cued <- factor(fig3_summary$cued)
fig3_summary$cond <- factor(fig3_summary$cond, levels = c("Baseline", "Prenap", "Postnap", "1-Week"))

ggplot(fig3_summary, aes(cond, mean, color=cued, group=cued)) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin = mean-se, ymax = mean+se), width=.1, size=1.2) +
  geom_line(size=1.2, linetype=c(1,1,1,1,2,2,2,2)) +
  ylim(0,.7) +
  scale_color_manual(values=c("black", "darkgrey")) +
  theme_classic() +
  easy_move_legend("bottom") +
  easy_remove_legend_title() +
  labs(x="", y = "D600 Bias Score") +
  easy_text_size(15)

```

# Figure 4
- not sure what it's plotting here
```{r}

```

# Figure 5
```{r}
fig5 <- humiston %>%
  select(sw_sx_rem, diff_biaschange)

ggplot(fig5, aes(sw_sx_rem, diff_biaschange)) +
  geom_point(size=4) +
  geom_smooth(method = "lm", se = FALSE, linetype=2, color="black") +
  theme_classic() +
  labs(x = "SWS x REM sleep duration (min)", y = "Differential bias change") +
  easy_text_size(15)

```

