---
title: "Belief Superiority Replication"
author: "Elizabeth Harris & Jay Van Bavel"
date: "5/8/2020"
output: pdf_document
---

```{r setup,include=FALSE}
library(ggplot2)
library(tidyverse)
library(lmerTest)
library(car)
library(TOSTER)
library(Hmisc)
library(optimx)
library(RColorBrewer)
library(reshape2)
library(psych)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=40),tidy=TRUE)

#setwd("~/~grad school/research/8 psych sci replication")

d=read.csv("harris/beliefsuperiority_all.csv")
d[] <- lapply(d, function(x) {
    if(is.factor(x)) as.numeric(as.character(x)) else x
})
```

*Jenny - ran first chunk and saved clean data*
Set up data

```{r}
#remove rows of those who did not agree to the consent form (and were directed to the end of survey)
d= filter(d,Q62 == 1)

#remove those who failed the attention check items and make a separate dataframe
d_attn= filter(d,AC_a==3) %>% 
  filter(AC_b==5)

#remove attention check items from dataframe
d_attn=dplyr::select(d_attn,-starts_with('AC'))

#Creating a mean dogmatism score
#First, items 2, 4, 5, 7, 10, 11, 13, 16, 18, 19 need to be reverse scored
d_attn$Q37_2 = recode(d_attn$Q37_2, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_4 = recode(d_attn$Q37_4, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_5 = recode(d_attn$Q37_5, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_7 = recode(d_attn$Q37_7, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_10 = recode(d_attn$Q37_10, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_11 = recode(d_attn$Q37_11, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_13 = recode(d_attn$Q37_13, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_16 = recode(d_attn$Q37_16, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_18 = recode(d_attn$Q37_18, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d_attn$Q37_19 = recode(d_attn$Q37_19, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')

dogscale=dplyr::select(d_attn,starts_with('Q37'))
d_attn$meanD=rowMeans(dogscale,na.rm = TRUE)

hist(d_attn$meanD)
#positive skew (not as many people high on dogmatism, mean is almost exactly midpoint of scale)

#Next, transform 4-pt attitude scales to 5-pt: vote, torture, affirmaction
#(5 - 1) * (x - 1) / (4 - 1) + 1
d_attn$vote_a = recode(d_attn$vote_a, '2=1; 3=2.3333; 4=3.6667; 5=5')
d_attn$torture_a = recode(d_attn$torture_a, '2=1; 3=2.3333; 4=3.6667; 5=5')
d_attn$affirmaction_a = recode(d_attn$affirmaction_a, '2=1; 3=2.3333; 4=3.6667; 5=5')

#Calculate an average attitude score per participant (for dogmatism analysis)
attitudes=dplyr::select(d_attn,ends_with('_a'))
d_attn$meanA=rowMeans(attitudes,na.rm = TRUE)

#mean center the variables
#dogmatism
d_attn$meanD_c= d_attn$meanD-mean(d_attn$meanD,na.rm=TRUE)
#mean attitude 
d_attn$meanA_c= d_attn$meanA-mean(d_attn$meanA,na.rm=TRUE)
#individual attitude ratings
d_attn$immigration_a_c=d_attn$immigration_a-mean(d_attn$immigration_a,na.rm=TRUE)
d_attn$abortion_a_c=d_attn$abortion_a-mean(d_attn$abortion_a,na.rm=TRUE)
d_attn$vote_a_c=d_attn$vote_a-mean(d_attn$vote_a,na.rm=TRUE)
d_attn$tax_a_c=d_attn$tax_a-mean(d_attn$tax_a,na.rm=TRUE)
d_attn$torture_a_c=d_attn$torture_a-mean(d_attn$torture_a,na.rm=TRUE)
d_attn$affirmaction_a_c=d_attn$affirmaction_a-mean(d_attn$affirmaction_a,na.rm=TRUE)
d_attn$military_a_c=d_attn$military_a-mean(d_attn$military_a,na.rm=TRUE)
d_attn$covidgov_a_c=d_attn$covidgov_a-mean(d_attn$covidgov_a,na.rm=TRUE)
#political orientation
d_attn$PO_c= d_attn$Q12-mean(d_attn$Q12,na.rm=TRUE)


#write_csv(d_attn, "clean_harris.csv")
```

Demographics - political affiliation

For a sample of 1300, a nationally politically representative sample is 31% D, 27% R and 39% I
according to one source (Gallup, https://news.gallup.com/poll/15370/party-affiliation.aspx )

In our sample we have: 

```{r}

#1= D, 2= R, 3=I
table(d_attn$Q16)
291/707
225/707
154/707

#from the total sample:
table(d$Q16)

```
Therefore, we have approximately the predicted proportion of Rs and over-sampled (but not extremely) the proportion of Ds

Scale characteristics: 
```{r}
#dogmatism
alpha(x=dogscale,na.rm=TRUE)
mean(d_attn$meanD,na.rm=TRUE)
sd(d_attn$meanD,na.rm=TRUE)

#attitude ratings
alpha(x=attitudes,na.rm=TRUE)
mean(d_attn$meanA,na.rm=TRUE)
sd(d_attn$meanA,na.rm=TRUE)

#belief superiority 
beliefs=dplyr::select(d_attn,ends_with('_b'))
meanB=rowMeans(beliefs,na.rm = TRUE)
alpha(x=beliefs,na.rm=TRUE)
mean(meanB,na.rm=TRUE)
sd(meanB,na.rm=TRUE)
```


--

Dogmatism analyses - 1

```{r}
#multiple regression in which dogmatism is regressed onto a linear 
#and quadratic term for average political attitude
D1= lm(meanD~meanA_c+I(meanA_c^2),d_attn)
summary(D1)

```

Dogmatism analyses - 2

```{r}
#same analysis but with the predictor being self-reported political orientation
D2= lm(meanD~PO_c+I(PO_c^2),d_attn)
summary(D2)

```

Dogmatism analyses - 3

```{r}
#simple t-test comparing the average dogmatism scores of self-identified Democrats and Republicans
dems=filter(d_attn,Q16==1)
reps=filter(d_attn,Q16==2)
t.test(dems$meanD,reps$meanD)

```
Dogmatism analyses - 4 (exploratory)

```{r}
#regress dogmatism onto the participants’ economic conservatism score and social conservatism score
d_attn$SC_c= d_attn$Q39 - mean(d_attn$Q39,na.rm=TRUE)
d_attn$EC_c= d_attn$Q40 - mean(d_attn$Q40,na.rm=TRUE)

SEdog=lm(meanD~SC_c+EC_c,d_attn)
summary(SEdog)
 
```

--

Belief superiority analyses

```{r}
#multilevel model: belief superiority regressed onto linear 
#and quadratic terms for attitude, with and without dogmatism covariate 
#random variables of subject and topic 

#first converting the dataset to long format 
d_attn$subject=c(1:nrow(d_attn))

d_attnlong <- bind_cols(d_attn %>% 
                        dplyr::select(.  , ends_with("_a_c"), subject,38:67,76) %>%
                        gather(. , topic, attitude_c, ends_with("_a_c")),
                      d_attn %>% dplyr::select(. ,ends_with("_b"), subject) %>%
                        gather(. , topic, beliefsup, ends_with("_b")),
                      d_attn %>% dplyr::select(. ,ends_with("_a"), subject) %>%
                        gather(. , topic, attitude, ends_with("_a"))
)

#model 1, without dogmatism 
beliefsup1= lmer(beliefsup~attitude_c+I(attitude_c^2)+
                   (1|subject)+
                   (1+attitude_c+I(attitude_c^2)|topic),d_attnlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup1)
coef(beliefsup1)$topic

#model 2, with dogmatism 
beliefsup2= lmer(beliefsup~attitude_c+I(attitude_c^2)+meanD_c+
                   (1|subject)+
                   (1+attitude_c+I(attitude_c^2)|topic),d_attnlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup2)

```
Equivalence testing 
```{r}
#starting with model 2
#this function requires SD, which I calculated with SE*sqrt(N)
#with the SE and N from the regression model output
0.07727*sqrt(706)
TOSTone(m = -0.02096,mu = 0,sd = 2.053115,n = 706,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

#then model 1
0.0767*sqrt(707)
TOSTone(m = -0.02822,mu = 0,sd = 2.039412,n = 707,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)
```


Figures 

```{r}
#dogmatism plot - 1
ggplot(d_attn, aes(x=meanA_c, y=meanD))+
  #geom_jitter(alpha=.5)+
  #theme(legend.position= "none") +
  geom_point(aes(y = meanD), position = position_jitter(width = .15), size = 2.5, alpha = 0.5) +
  labs(x='Average Attitude', y='Dogmatism') +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 2) +
     theme_minimal()+
  theme(axis.title.y = element_text(size=16, face="bold"))+
  theme(axis.title.x = element_text(size=16, face="bold"))+
  theme(axis.text.y=element_text(color = "black", size = 14))+
  theme(axis.text.x=element_text(color = "black", size = 14))+
  theme(legend.text = element_text(color = "black", size = 14))+
  theme(legend.title = element_text(color = "black", size = 14))+
  theme(axis.line= element_line(color="black")) +
  theme(axis.ticks.y = element_line(color="black")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(strip.text.x=element_text(color = "black", size = 14, face="bold"))+
  xlim(c(-2,2))+
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9),lim=c(1,9))

#dogmatism plot - 2
ggplot(d_attn, aes(x=PO_c, y=meanD,color=PO_c))+
  #geom_jitter(alpha=.5)+
  #theme(legend.position= "none") +
  geom_point(aes(y = meanD), position = position_jitter(width = .15), size = 2.5, alpha = 0.6) +
  stat_summary(fun.y=mean, geom='point', size=2, color="black") +
  stat_summary(fun.data = mean_cl_boot,geom='errorbar', fun.args=list(conf.int=.95), 
               size=1.5, aes(width=.3), color="black")+
  labs(x='Political Orientation', y='Dogmatism') +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 2) +
   theme_minimal()+
  theme(axis.title.y = element_text(size=16, face="bold"))+
  theme(axis.title.x = element_text(size=16, face="bold"))+
  theme(axis.text.y=element_text(color = "black", size = 14))+
  theme(axis.text.x=element_text(color = "black", size = 14))+
  theme(legend.text = element_text(color = "black", size = 14))+
  theme(legend.title = element_text(color = "black", size = 14))+
  theme(axis.line= element_line(color="black")) +
  theme(axis.ticks.y = element_line(color="black")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(strip.text.x=element_text(color = "black", size = 14, face="bold")) +
  theme(legend.position = "none")+
  scale_x_continuous(breaks = c(-3,-2,-1,0,1,2,3),lim=c(-3.1,3.1))+
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9),lim=c(1,9))

#belief superiority plot 
d_attnlong$attitude=as.factor(d_attnlong$attitude)
forplot= d_attnlong[which(!is.na(d_attnlong$attitude)),]

raincloud_theme = theme(
  text = element_text(size = 10),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  axis.text = element_text(size = 14),
  axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title=element_text(size=16),
  legend.text=element_text(size=16),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 16),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

ggplot(forplot, aes(x=attitude, y=beliefsup,color=attitude))+
  theme(legend.position= "none") +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = beliefsup, color = attitude), position = position_jitter(width = .15), 
             size = 1.5, alpha = 0.2) +
   stat_summary(fun.y=mean, size=2, color="black",geom="line", aes(group = 1)) +
  stat_summary(fun.y=mean, size=2, color="black",geom="point", aes(group = 1)) +
  stat_summary(fun.data = mean_cl_boot,geom='errorbar', fun.args=list(conf.int=.95), 
               size=1.5, aes(width=.3), color="black")+
  labs(x='Attitude', y='Belief Superiority') +
   theme_minimal()+
  theme(axis.title.y = element_text(size=16, face="bold"))+
  theme(axis.title.x = element_text(size=16, face="bold"))+
  theme(axis.text.y=element_text(color = "black", size = 14))+
  theme(axis.text.x=element_text(color = "black", size = 14))+
  theme(legend.text = element_text(color = "black", size = 14))+
  theme(legend.title = element_text(color = "black", size = 14))+
  theme(axis.line= element_line(color="black")) +
  theme(axis.ticks.y = element_line(color="black")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(strip.text.x=element_text(color = "black", size = 14, face="bold"))+
  theme(legend.position = "none")+
  scale_x_discrete(labels = c("1","2","2.3","3","3.7","4","5"))

```





----- SUPPLEMENTARY ANALYSES -----




Belief superiority MLMs WITHOUT quadratic term in topic random effect

```{r}
#the two models while without the quadratic term in topic 
#model without dogmatism 
beliefsup3= lmer(beliefsup~attitude_c+I(attitude_c^2)+
                   (1|subject)+
                   (1+attitude_c|topic),d_attnlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup3)
#model with dogmatism 
beliefsup4= lmer(beliefsup~attitude_c+I(attitude_c^2)+meanD_c+
                   (1|subject)+
                   (1+attitude_c|topic),d_attnlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup4)
```





Exploratory breakdown by topic

```{r}
#per topic

immigration= lm(immigration_b~immigration_a_c+I(immigration_a_c^2),d_attn)
summary(immigration)
#linear sig, more for C

abortion= lm(abortion_b~abortion_a_c+I(abortion_a_c^2),d_attn)
summary(abortion)
#no linear

vote= lm(vote_b~vote_a_c+I(vote_a_c^2),d_attn)
summary(vote)
#linear sig, more for C

tax= lm(tax_b~tax_a_c+I(tax_a_c^2),d_attn)
summary(tax)
#linear sig, more for C

torture= lm(torture_b~torture_a_c+I(torture_a_c^2),d_attn)
summary(torture)
#no linear

affirmaction= lm(affirmaction_b~affirmaction_a_c+I(affirmaction_a_c^2),d_attn)
summary(affirmaction)
#no linear

military= lm(military_b~military_a_c+I(military_a_c^2),d_attn)
summary(military)
#no linear, trending for more for L

covidgov= lm(covidgov_b~covidgov_a_c+I(covidgov_a_c^2),d_attn)
summary(covidgov)
#linear, more for L 

#although, with bonferroni correction for the 8 regressions here (0.05/8= 0.00625), 
#tax no longer has a significant linear term
```



All the analyses with the whole dataset (including those who failed attention check)

```{r}
d=dplyr::select(d,-starts_with('AC'))
d$Q37_2 = recode(d$Q37_2, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_4 = recode(d$Q37_4, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_5 = recode(d$Q37_5, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_7 = recode(d$Q37_7, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_10 = recode(d$Q37_10, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_11 = recode(d$Q37_11, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_13 = recode(d$Q37_13, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_16 = recode(d$Q37_16, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_18 = recode(d$Q37_18, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
d$Q37_19 = recode(d$Q37_19, '1=9; 2=8; 3=7; 4=6; 6=4; 7=3; 8=2; 9=1')
dogscale=dplyr::select(d,starts_with('Q37'))
d$meanD=rowMeans(dogscale,na.rm = TRUE)
d$vote_a = recode(d$vote_a, '2=1; 3=2.3333; 4=3.6667; 5=5')
d$torture_a = recode(d$torture_a, '2=1; 3=2.3333; 4=3.6667; 5=5')
d$affirmaction_a = recode(d$affirmaction_a, '2=1; 3=2.3333; 4=3.6667; 5=5')
attitudes=dplyr::select(d,ends_with('_a'))
d$meanA=rowMeans(attitudes,na.rm = TRUE)
d$meanD_c= d$meanD-mean(d$meanD,na.rm=TRUE)
d$meanA_c= d$meanA-mean(d$meanA,na.rm=TRUE)
d$immigration_a_c=d$immigration_a-mean(d$immigration_a,na.rm=TRUE)
d$abortion_a_c=d$abortion_a-mean(d$abortion_a,na.rm=TRUE)
d$vote_a_c=d$vote_a-mean(d$vote_a,na.rm=TRUE)
d$tax_a_c=d$tax_a-mean(d$tax_a,na.rm=TRUE)
d$torture_a_c=d$torture_a-mean(d$torture_a,na.rm=TRUE)
d$affirmaction_a_c=d$affirmaction_a-mean(d$affirmaction_a,na.rm=TRUE)
d$military_a_c=d$military_a-mean(d$military_a,na.rm=TRUE)
d$covidgov_a_c=d$covidgov_a-mean(d$covidgov_a,na.rm=TRUE)
d$PO_c= d$Q12-mean(d$Q12,na.rm=TRUE)

##dogmatism 
D1= lm(meanD~meanA_c+I(meanA_c^2),d)
summary(D1)
D2= lm(meanD~PO_c+I(PO_c^2),d)
summary(D2)
dems=filter(d,Q16==1)
reps=filter(d,Q16==2)
t.test(dems$meanD,reps$meanD)
d$SC_c= d$Q39 - mean(d$Q39,na.rm=TRUE)
d$EC_c= d$Q40 - mean(d$Q40,na.rm=TRUE)
SEdog=lm(meanD~SC_c+EC_c,d)
summary(SEdog)

#beliefsup
d$subject=c(1:nrow(d))
dlong <- bind_cols(d %>% 
                        dplyr::select(.  , ends_with("_a_c"), subject,38:67,76) %>%
                        gather(. , topic, attitude_c, ends_with("_a_c")),
                      d %>% dplyr::select(. ,ends_with("_b"), subject) %>%
                        gather(. , topic, beliefsup, ends_with("_b"))
)

beliefsup1= lmer(beliefsup~attitude_c+I(attitude_c^2)+
                   (1|subject)+
                   (1+attitude_c+I(attitude_c^2)|topic),dlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup1)
coef(beliefsup1)$topic

beliefsup2= lmer(beliefsup~attitude_c+I(attitude_c^2)+meanD_c+
                   (1|subject)+
                   (1+attitude_c+I(attitude_c^2)|topic),dlong,
                 control =  lmerControl(optimizer="bobyqa"))
summary(beliefsup2)

#starting with model 2
#this function requires SD, which I calculated with SE*sqrt(N)
#with the SE and N from the regression model output
0.0638*sqrt(1317)
TOSTone(m = 0.0352,mu = 0,sd = 2.31533,n = 1317,low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

#then model 1
0.06298*sqrt(1319)
TOSTone(m = -0.04131,mu = 0,sd = 2.28731,n = 1319,low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)
```

Equivalence testing using 1. the number of trials as N in the analysis and 2. using the number of scales as N in the analysis 
(in our paper, we report the TOSTs using number of participants as N)

```{r}
#with number of trials
#starting with model 2
0.07727*sqrt(5633)
TOSTone(m = -0.02096,mu = 0,sd = 2.05311,n = 5633,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

#then model 1
0.0767*sqrt(5641)
TOSTone(m = -0.02822,mu = 0,sd = 2.03941,n = 5641,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

#with number of scales 
0.07727*sqrt(8)
TOSTone(m = -0.02096,mu = 0,sd = 2.05311,n = 8,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

0.0767*sqrt(8)
TOSTone(m = -0.02822,mu = 0,sd = 2.03941,n = 8,
        low_eqbound_d = -0.1,high_eqbound_d = 0.1,alpha = 0.05)

```

